Direction-Free In-Air Signature Verification Using WIFI CSI Signal

### 2019-05-17 190410_Paper_ACPR/paper_v1.tex
Advp_a3: done_v1

\subsection{ConvNets}
% description of convnet
Convolutional Neural Networks is a specal case of MLP and it has unified feature extractor and classifier in one network. It has been widely applied to visual objects such as image or video or 2D array input. Several factors make ConvNets attractive in image related tasks.
Local connectivity captures local correlation property of image. It is applycable by using ConvNet filter.
Weight sharing helps to reduce the number of weights in feature maps.
Also, CUDA libraries makes the tranining feature maps easier to reduce training time.
%

@@

In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
An overview of the proposed system is shown in Fig.1.
% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{methods1.eps}
    \caption{Overview of the proposed system} \label{method1}
\end{figure}

% purpose of the system
This system receives two Wi-Fi CSI signals as input.
The main purpose of the system is to verify if two input signals are of the same signature.

% main purpose1: interpreting CSI 
Our system must have the ability to distinguish signatures by reading Wi-Fi CSI signals.
% verification model
The verification model learns to identify input pairs according to the probability that they belong to the same class or different classes.\cite{koch2015siamese}

% main purpose2: direction free
Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.

@@

% structure of siamese network
When two processed signals come as the input, they are put to 2 symmetric ConvNet. 
%Symmetric Architecture
Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that help to classify signatures. some may be heavily influenced by the direction in which the signature was entered. Structure of the network is shown in Fig.2.
% Figure 2
\begin{figure}
    \includegraphics[width=\textwidth]{network1.eps}
    \caption{Structure of Siamese network} \label{network1}
\end{figure}
% weight tying
We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
It was also designed to have the same weight on the symmetrical CNN network.

>>>>

\subsection{ConvNets}
% description of convnet
Convolutional Neural Networks is a specal case of Multi Layer Perceptron and it has unified feature extractor and classifier in one network. It has been widely applied to visual objects such as image, video or 2D array input. Several factors make ConvNets attractive in image related tasks.
Local connectivity captures local correlation property of image. It is applycable by using ConvNet filter.Weight sharing helps to reduce the number of weights in feature maps.
Also, CUDA libraries makes the tranining feature maps easier to reduce training time.
%

@@

In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature which utilizes the Siamese network learning.
\iffalse
An overview of the proposed system is shown in Fig.1.
% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{methods1.eps}
    \caption{Overview of the proposed system} \label{method1}
\end{figure}
\fi
Essentially, we train the verification model to identify the input pairs according to the probability on whether they belong to the same class or different classes.\cite{koch2015siamese} Subsequently, the

\iffalse
% main purpose2: direction free
Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
\fi

@@

% structure of siamese network
When two processed signals come as the input, they are put to 2 symmetric ConvNet. 
%Symmetric Architecture
Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that help to classify signatures. some may be heavily influenced by the direction in which the signature was entered. Structure of the network is shown in Fig.2.
% Figure 2
\begin{figure}
    \includegraphics[width=\textwidth]{network2.eps}
    \caption{Structure of Siamese network} \label{network2}
\end{figure}
% weight tying
We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
It was also designed to have the same weight on the symmetrical CNN network.
